Illustrating Good Practice in {\LaTeX}

### 2022-03-25 articles/good_practice.tex
new css colors working

\begin{figure}[H]
\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
\centering
\begin{tikzpicture}[scale=1.1]
    \draw[BLACK, ->] (-4,0) -- (9,0) node[BLACK, anchor=west] {$z$};
    \draw[BLACK, ->] (0,-1.4) -- (0,1.4) node[BLACK, anchor=south] {$g(z,0)$};
    \draw[BLUE, thick] (-4.6,1) cos (-3.6,0);
    \draw[BLUE, thick] (-3.6,0) sin (-2.6,-1);
    \draw[BLUE, thick] (-2.6,-1) cos (-1.6,0);
    \draw[BLUE, thick] (-1.6,0) sin (-0.6,1);
    \draw[BLUE, thick] (-0.6,1) cos (0.6,0);
    \draw[BLUE, thick] (0.6,0) sin (1.6,-1);
    \draw[BLUE, thick] (1.6,-1) cos (2.6,0);
    \draw[BLUE, thick] (2.6,0) sin (3.6,1);
    \draw[BLUE, thick] (3.6,1) cos (4.6,0);
    \draw[BLUE, thick] (4.6,0) sin (5.6,-1);
    \draw[BLUE, thick] (5.6,-1) cos (6.6,0);
    \draw[BLUE, thick] (6.6,0) sin (7.6,1);
    %
    \draw[BLACK, ->] (3.6,0) -- (3.6,1) node[BLACK, left, midway] {\small $A$};
    \draw[BLACK] (3.2,1) -- (4.0,1);
    %
    \filldraw[BLACK] (-0.6,1) circle (0.1);
    \node[BLACK, above] at (-3.6,1.3) {\parbox[c]{0.2\textwidth}{\begin{center} \small Central \\ maximum \end{center}}};
    \draw[BLACK, thick, <-] (-0.7,1.1) -- (-3,2);
    %
    \draw[BLACK, dashed] (-0.6,1) -- (-0.6,0);
	\draw[BLACK, thick, decoration={brace, mirror, raise=5pt}, decorate] (-0.6,0) -- (0,0) node[black, midway, below=6pt] {\small $\delta/k$};
	%
	\draw[BLACK, ->] (5,1.6) -- (6.6,1.6) node[BLACK, midway, above] {\small $v$};
	%
	\draw[BLACK] (1.6,-1) -- (1.6,-1.5);
	\draw[BLACK] (5.6,-1) -- (5.6,-1.5);
	\draw[BLACK, <->] (1.6,-1.25) -- (5.6,-1.25) node[BLACK, midway, below] {\small $\lambda$};
\end{tikzpicture}
\caption{A sinusoidal wave train. With the passage of time, the entire wave train proceeds to the right.}
\label{fig:sinusoidalwave}
\end{figure}

@@

\begin{figure}[H]
\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
\centering
\begin{tikzpicture}[xscale=1,yscale=1]
    % Draw outside rectangle
    \draw[BLACK] (-2,-2) rectangle (14,10);
    % Draw lattice points
    \foreach \a in {0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12}
    {
        \foreach \b in {0, 1, 2, 3, 4, 5, 6, 7, 8}
        {
            \filldraw[BLACK] (\a, \b) circle (2pt);
        }
    }
    \node[BLACK, anchor=north] at (0,0) {$x_0$};
    \node[BLACK, anchor=north] at (1,0) {$x_1$};
    \node[BLACK, anchor=north] at (11,0) {$x_{N - 1}$};
    \node[BLACK, anchor=north] at (12,0) {$x_N$};
    \node[BLACK, anchor=east] at (0,0) {$y_0$};
    \node[BLACK, anchor=east] at (0,1) {$y_1$};
    \node[BLACK, anchor=east] at (0,7) {$y_{M - 1}$};
    \node[BLACK, anchor=east] at (0,8) {$y_M$};
    \draw[BLACK, <->] (7,-0.2) -- (8,-0.2);
    \node[BLACK, below] at (7.5,-0.2) {$h$};
    \draw[BLACK, <->] (-0.2,4) -- (-0.2,5);
    \node[BLACK, left] at (-0.2,4.5) {$h$};
    \filldraw[RED] (6,4) circle (2.5pt) node[anchor=south west] {$V_{n,m}$};
    \draw[RED] (6,3) -- (6,4) -- (6,5);
    \draw[RED] (5,4)-- (6,4) -- (7,4);
    \filldraw[BLUE] (7,4) circle (2.5pt) node[anchor=north west] {$V_{n+1,m}$};
    \filldraw[BLUE] (5,4) circle (2.5pt) node[anchor=south east] {$V_{n-1,m}$};
    \filldraw[BLUE] (6,3) circle (2.5pt) node[anchor=north] {$V_{n,m+1}$};
    \filldraw[BLUE] (6,5) circle (2.5pt) node[anchor=south] {$V_{n,m-1}$};
    \draw[BLACK, <->] (0,8.3) -- (12,8.3);
    \node[BLACK, above] at (6,8.3) {$w$};
    \draw[BLACK, <->] (12.3,0) -- (12.3,8);
    \node[BLACK, right] at (12.3,4) {$\ell$};
\end{tikzpicture}
\caption{A two-dimensional lattice of points.}
\label{fig:latticegrid}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}[scale=0.5]
    % primary colors
    \fill[BLUE] (30:2.4) circle (4);
    \fill[RED] (150:2.4) circle (4);
    \fill[GREEN] (270:2.4) circle (4);
    % secondary colors
    \begin{scope} % red + blue = purple
        \clip (150:2.4) circle (4);
        \fill[PURPLE] (30:2.4) circle (4);
    \end{scope}
    \begin{scope} % red + green = yellow
        \clip (270:2.4) circle (4);
        \fill[YELLOW] (150:2.4) circle (4);
    \end{scope}
    \begin{scope} green + blue = teal
        \clip (30:2.4) circle (4);
        \fill[TEAL] (270:2.4) circle (4);
    \end{scope}
    % red + blue + green = white
    \begin{scope}
        \clip (30:2.4) circle (4);
        \clip (150:2.4) circle (4);
        \fill[WHITE] (270:2.4) circle (4);
    \end{scope}
\end{tikzpicture}
\end{figure}

@@

Here are some cool circled numbers. The first argument is whatever is to be circled, and the \colorbox{TEAL}{second argument} is the background color. The \colorbox{PURPLE}{third argument} is the outline color, and the \colorbox{RED}{fourth argument} is color of the first argument.

\begin{figure}[H]
\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
\centering
\begin{tikzpicture}[scale=1.6]
    \foreach \c in {0, 1, 2, 3, 4, 5, 6, 7, 8, 9}
    {
        \node at (\c,0) {\Huge\circled{\c}{TEAL}{PURPLE}{RED}};
    }
\end{tikzpicture}
\caption*{Isn't this cool?}
\end{figure}

These circled numbers work in equations too!
\begin{equation*}
    \bigints_{\circled{$a$}{PINK}{BLACK}{BLACK}}^{\circled{$b$}{GOLDC}{BLACK}{BLACK}} \Scale[2]{f(x)} \Scale[2]{dx} \hspace{1em} \Scale[2]{+} \hspace{1em} \bigints_{\circled{$b$}{GOLDC}{BLACK}{BLACK}}^{\circled{$a$}{PINK}{BLACK}{BLACK}} \Scale[2]{f(x)} \Scale[2]{dx} \hspace{1em} \Scale[2]{=} \hspace{1em} \Scale[2]{\circled{0}{GREEN}{RED}{BLACK}}
\end{equation*}

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}
    \coordinate (vertex1) at (4,0);
    \coordinate (vertex2) at (2,3.464102);
    \coordinate (vertex3) at (-2,3.464102);
    \coordinate (vertex4) at (-4,0);
    \coordinate (vertex5) at (-2,-3.464102);
    \coordinate (vertex6) at (2,-3.464102);
    %
    \node at (vertex1) (nodeV1) {\Huge\circled{1}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex2) (nodeV2) {\Huge\circled{2}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex3) (nodeV3) {\Huge\circled{3}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex4) (nodeV4) {\Huge\circled{4}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex5) (nodeV5) {\Huge\circled{5}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex6) (nodeV6) {\Huge\circled{6}{ORANGE}{RED}{DARKBLUE}};
    %
    \draw[BLACK, ultra thick, <->] (nodeV1) -- (nodeV2);
    \draw[BLACK, ultra thick, ->] (nodeV2) -- (nodeV3);
    \draw[BLACK, ultra thick, <->] (nodeV3) -- (nodeV4);
    \draw[BLACK, ultra thick, ->] (nodeV4) -- (nodeV5);
    \draw[BLACK, ultra thick, <->] (nodeV5) -- (nodeV6);
    \draw[BLACK, ultra thick, <->] (nodeV1) -- (nodeV4);
    \draw[BLACK, ultra thick, ->] (nodeV1) -- (nodeV3);
    \draw[BLACK, ultra thick, ->] (nodeV4) -- (nodeV6);
\end{tikzpicture}
\end{figure}

@@

\begin{table}[H]
\centering
\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
\caption{Energies and corresponding degeneracies of the 3D QHO}
\begin{tabular}{@{}ccc@{}}
\toprule
State & Energy & Degeneracy \\ \midrule
\multicolumn{1}{c|}{Ground state} & \multicolumn{1}{c|}{$\displaystyle \frac{3}{2}\hbar\omega$} & 1 \\[1em]
\multicolumn{1}{c|}{First excited state} & \multicolumn{1}{c|}{$\displaystyle \frac{5}{2}\hbar\omega$} & 3 \\[1em]
\multicolumn{1}{c|}{Second excited state} & \multicolumn{1}{c|}{$\displaystyle \frac{7}{2}\hbar\omega$} & 6 \\[1em]
\multicolumn{1}{c|}{Third excited state} & \multicolumn{1}{c|}{$\displaystyle \frac{9}{2}\hbar\omega$} & 10 \\ \bottomrule
\end{tabular}
\end{table}

>>>>

\begin{figure}[H]
\captionsetup{width=0.8\textwidth,labelfont={color=black,bf},textfont={color=black}}
\centering
\begin{tikzpicture}[scale=1.1]
    \draw[black, ->] (-4,0) -- (9,0) node[black, anchor=west] {$z$};
    \draw[black, ->] (0,-1.4) -- (0,1.4) node[black, anchor=south] {$g(z,0)$};
    \draw[blue, thick] (-4.6,1) cos (-3.6,0);
    \draw[blue, thick] (-3.6,0) sin (-2.6,-1);
    \draw[blue, thick] (-2.6,-1) cos (-1.6,0);
    \draw[blue, thick] (-1.6,0) sin (-0.6,1);
    \draw[blue, thick] (-0.6,1) cos (0.6,0);
    \draw[blue, thick] (0.6,0) sin (1.6,-1);
    \draw[blue, thick] (1.6,-1) cos (2.6,0);
    \draw[blue, thick] (2.6,0) sin (3.6,1);
    \draw[blue, thick] (3.6,1) cos (4.6,0);
    \draw[blue, thick] (4.6,0) sin (5.6,-1);
    \draw[blue, thick] (5.6,-1) cos (6.6,0);
    \draw[blue, thick] (6.6,0) sin (7.6,1);
    %
    \draw[black, ->] (3.6,0) -- (3.6,1) node[black, left, midway] {\small $A$};
    \draw[black] (3.2,1) -- (4.0,1);
    %
    \filldraw[black] (-0.6,1) circle (0.1);
    \node[black, above] at (-3.6,1.3) {\parbox[c]{0.2\textwidth}{\begin{center} \small Central \\ maximum \end{center}}};
    \draw[black, thick, <-] (-0.7,1.1) -- (-3,2);
    %
    \draw[black, dashed] (-0.6,1) -- (-0.6,0);
	\draw[black, thick, decoration={brace, mirror, raise=5pt}, decorate] (-0.6,0) -- (0,0) node[black, midway, below=6pt] {\small $\delta/k$};
	%
	\draw[black, ->] (5,1.6) -- (6.6,1.6) node[black, midway, above] {\small $v$};
	%
	\draw[black] (1.6,-1) -- (1.6,-1.5);
	\draw[black] (5.6,-1) -- (5.6,-1.5);
	\draw[black, <->] (1.6,-1.25) -- (5.6,-1.25) node[black, midway, below] {\small $\lambda$};
\end{tikzpicture}
\caption{A sinusoidal wave train. With the passage of time, the entire wave train proceeds to the right.}
\label{fig:sinusoidalwave}
\end{figure}

@@

\begin{figure}[H]
\captionsetup{width=0.8\textwidth,labelfont={color=black,bf},textfont={color=black}}
\centering
\begin{tikzpicture}[xscale=1,yscale=1]
    % Draw outside rectangle
    \draw[black] (-2,-2) rectangle (14,10);
    % Draw lattice points
    \foreach \a in {0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12}
    {
        \foreach \b in {0, 1, 2, 3, 4, 5, 6, 7, 8}
        {
            \filldraw[black] (\a, \b) circle (2pt);
        }
    }
    \node[black, anchor=north] at (0,0) {$x_0$};
    \node[black, anchor=north] at (1,0) {$x_1$};
    \node[black, anchor=north] at (11,0) {$x_{N - 1}$};
    \node[black, anchor=north] at (12,0) {$x_N$};
    \node[black, anchor=east] at (0,0) {$y_0$};
    \node[black, anchor=east] at (0,1) {$y_1$};
    \node[black, anchor=east] at (0,7) {$y_{M - 1}$};
    \node[black, anchor=east] at (0,8) {$y_M$};
    \draw[black, <->] (7,-0.2) -- (8,-0.2);
    \node[black, below] at (7.5,-0.2) {$h$};
    \draw[black, <->] (-0.2,4) -- (-0.2,5);
    \node[black, left] at (-0.2,4.5) {$h$};
    \filldraw[red] (6,4) circle (2.5pt) node[anchor=south west] {$V_{n,m}$};
    \draw[red] (6,3) -- (6,4) -- (6,5);
    \draw[red] (5,4)-- (6,4) -- (7,4);
    \filldraw[blue] (7,4) circle (2.5pt) node[anchor=north west] {$V_{n+1,m}$};
    \filldraw[blue] (5,4) circle (2.5pt) node[anchor=south east] {$V_{n-1,m}$};
    \filldraw[blue] (6,3) circle (2.5pt) node[anchor=north] {$V_{n,m+1}$};
    \filldraw[blue] (6,5) circle (2.5pt) node[anchor=south] {$V_{n,m-1}$};
    \draw[black, <->] (0,8.3) -- (12,8.3);
    \node[black, above] at (6,8.3) {$w$};
    \draw[black, <->] (12.3,0) -- (12.3,8);
    \node[black, right] at (12.3,4) {$\ell$};
\end{tikzpicture}
\caption{A two-dimensional lattice of points.}
\label{fig:latticegrid}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}[scale=0.5]
    % primary colors
    \fill[blue] (30:2.4) circle (4);
    \fill[red] (150:2.4) circle (4);
    \fill[lime] (270:2.4) circle (4);
    % secondary colors
    \begin{scope} % red + blue = purple
        \clip (150:2.4) circle (4);
        \fill[magenta] (30:2.4) circle (4);
    \end{scope}
    \begin{scope} % red + green = yellow
        \clip (270:2.4) circle (4);
        \fill[yellow] (150:2.4) circle (4);
    \end{scope}
    \begin{scope} green + blue = teal
        \clip (30:2.4) circle (4);
        \fill[cyan] (270:2.4) circle (4);
    \end{scope}
    % red + blue + green = white
    \begin{scope}
        \clip (30:2.4) circle (4);
        \clip (150:2.4) circle (4);
        \fill[white] (270:2.4) circle (4);
    \end{scope}
\end{tikzpicture}
\end{figure}

@@

Here are some cool circled numbers. The first argument is whatever is to be circled, and the \colorbox{cyan}{second argument} is the background color. The \colorbox{purple}{third argument} is the outline color, and the \colorbox{red}{fourth argument} is color of the first argument.

\begin{figure}[H]
\captionsetup{width=0.8\textwidth,labelfont={color=black,bf},textfont={color=black}}
\centering
\begin{tikzpicture}[scale=1.6]
    \foreach \c in {0, 1, 2, 3, 4, 5, 6, 7, 8, 9}
    {
        \node at (\c,0) {\Huge\circled{\c}{cyan}{purple}{red}};
    }
\end{tikzpicture}
\caption*{Isn't this cool?}
\end{figure}

These circled numbers work in equations too!
\begin{equation*}
    \bigints_{\circled{$a$}{pink}{black}{black}}^{\circled{$b$}{goldenrod}{black}{black}} \Scale[2]{f(x)} \Scale[2]{dx} \hspace{1em} \Scale[2]{+} \hspace{1em} \bigints_{\circled{$b$}{goldenrod}{black}{black}}^{\circled{$a$}{pink}{black}{black}} \Scale[2]{f(x)} \Scale[2]{dx} \hspace{1em} \Scale[2]{=} \hspace{1em} \Scale[2]{\circled{0}{lime}{red}{black}}
\end{equation*}

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}
    \coordinate (vertex1) at (4,0);
    \coordinate (vertex2) at (2,3.464102);
    \coordinate (vertex3) at (-2,3.464102);
    \coordinate (vertex4) at (-4,0);
    \coordinate (vertex5) at (-2,-3.464102);
    \coordinate (vertex6) at (2,-3.464102);
    %
    \node at (vertex1) (nodeV1) {\Huge\circled{1}{orange}{red}{nkostincolor}};
    \node at (vertex2) (nodeV2) {\Huge\circled{2}{orange}{red}{nkostincolor}};
    \node at (vertex3) (nodeV3) {\Huge\circled{3}{orange}{red}{nkostincolor}};
    \node at (vertex4) (nodeV4) {\Huge\circled{4}{orange}{red}{nkostincolor}};
    \node at (vertex5) (nodeV5) {\Huge\circled{5}{orange}{red}{nkostincolor}};
    \node at (vertex6) (nodeV6) {\Huge\circled{6}{orange}{red}{nkostincolor}};
    %
    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV2);
    \draw[black, ultra thick, ->] (nodeV2) -- (nodeV3);
    \draw[black, ultra thick, <->] (nodeV3) -- (nodeV4);
    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV5);
    \draw[black, ultra thick, <->] (nodeV5) -- (nodeV6);
    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV4);
    \draw[black, ultra thick, ->] (nodeV1) -- (nodeV3);
    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV6);
\end{tikzpicture}
\end{figure}

@@

\begin{table}[H]
\centering
\captionsetup{width=0.8\textwidth,labelfont={color=black,bf},textfont={color=black}}
\caption{Energies and corresponding degeneracies of the 3D QHO}
\begin{tabular}{@{}ccc@{}}
\toprule
State & Energy & Degeneracy \\ \midrule
\multicolumn{1}{c|}{Ground state} & \multicolumn{1}{c|}{$\displaystyle \frac{3}{2}\hbar\omega$} & 1 \\[1em]
\multicolumn{1}{c|}{First excited state} & \multicolumn{1}{c|}{$\displaystyle \frac{5}{2}\hbar\omega$} & 3 \\[1em]
\multicolumn{1}{c|}{Second excited state} & \multicolumn{1}{c|}{$\displaystyle \frac{7}{2}\hbar\omega$} & 6 \\[1em]
\multicolumn{1}{c|}{Third excited state} & \multicolumn{1}{c|}{$\displaystyle \frac{9}{2}\hbar\omega$} & 10 \\ \bottomrule
\end{tabular}
\end{table}
